% --------------------------------------------------------------------------------------------------------------
%
% Copyright 2020-2022 Robert Bosch GmbH

% Licensed under the Apache License, Version 2.0 (the "License");
% you may not use this file except in compliance with the License.
% You may obtain a copy of the License at

% http://www.apache.org/licenses/LICENSE-2.0

% Unless required by applicable law or agreed to in writing, software
% distributed under the License is distributed on an "AS IS" BASIS,
% WITHOUT WARRANTIES OR CONDITIONS OF ANY KIND, either express or implied.
% See the License for the specific language governing permissions and
% limitations under the License.
%
% --------------------------------------------------------------------------------------------------------------


\section{Introduction}

\textbf{RobotFramework\_DBus} is a Python extension library for Robot Framework. It is designed to support the automation testing of DBus services. The library provides a set of keywords that enable testing of DBus methods and signals using both synchronous and asynchronous mechanisms.

Built upon the Python \textit{dasbus} library, \textbf{RobotFramework\_DBus} simplifies the process of interacting with DBus services and facilitates efficient testing of their functionality. It offers a comprehensive set of features to streamline the testing process and ensure the reliability of DBus-based applications.

\section{Key Features}

\begin{itemize}
  \item Integration with Robot Framework: \textbf{RobotFramework\_DBus} seamlessly integrates with Robot Framework, allowing you to leverage its powerful test automation capabilities for DBus services.
  \item DBus Service Automation: With \textbf{RobotFramework\_DBus}, you can easily automate the testing of DBus services. It provides a range of keywords specifically designed for this purpose.
  \item Testing DBus Methods and Signals: The library enables you to test both DBus methods and signals. You can validate the behavior of DBus methods and monitor the emission of signals during the testing process.
  \item Synchronous and Asynchronous Testing: \textbf{RobotFramework\_DBus} supports both synchronous and asynchronous testing approaches. You can choose the appropriate mechanism based on your testing requirements.
\end{itemize}

Whether you are testing a single DBus service or a complex system of interconnected services, \textbf{RobotFramework\_DBus} offers a reliable and efficient solution for DBus automation testing. It empowers you to ensure the quality and robustness of your DBus-based applications.

